---
title: "Plot Script Dataset Attributes"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset attribute `plot_script`

Here are the ones found with singular dataset matches. The R code for insertion into the `get_{dataset}.R` script is provided and a short uniquely identifiable title for the tab display is also shown.

```{r}
librarian::shelf(
  dplyr, glue, here, NOAA-EDAB/ecodata, DT, purrr, readr, readxl, stringr, tidyr)

dir_ecodata <- "/share/github/ecodata_edab"
dir_plotr   <- glue("{dir_ecodata}/chunk-scripts")

datatable_btns <- function(...){
  datatable(
    ..., 
    escape = F,
    extensions = 'Buttons', options = list(
      dom = 'Bfrtip',
      buttons = c('copy', 'csv', 'excel'))) }

ds <- data(package = "ecodata") %>% .$results %>% .[,3]
#datatable(tibble(dataset_id = ds))

d <- tibble(
  file_plotr   = list.files(dir_plotr, "\\.R$"),
  component    = str_replace(file_plotr, "^(.*)_(.*?).Rmd-(.*)\\.R$", "\\1"),
  cmp          = recode(
    component,
    human_dimensions = "hd",
    LTL              = "ltl",
    macrofauna       = "mf"),
  region       = str_replace(file_plotr, "^(.*)_(.*?).Rmd-(.*)\\.R$", "\\2"),
  dataset_dash = str_replace(file_plotr, "^(.*)_(.*?).Rmd-(.*)\\.R$", "\\3"),
  dataset_sub  = str_replace_all(dataset_dash, "-", "_"),
  dataset_id   = map_chr(dataset_sub, function(x){
    y <- str_extract(x, ds) %>% na.omit()
    y <- ifelse(length(y) == 1, y, NA)
    y }),
  part       = map2_chr(dataset_sub, dataset_id, function(sub, id){
    s <- str_replace(sub, id, "") %>% 
      str_replace("^_", "") %>% 
      str_replace("_$", "") %>% 
      str_replace_all("_", "-") %>% 
      str_replace_all("[-]{2,}", "-")
    ifelse(nchar(s) > 0, s, NA) })) %>% 
  mutate(
    title = pmap_chr(., function(cmp, region, part, ...){
      paste(na.omit(c(cmp, region, part)), collapse = "_") })) %>% 
  arrange(dataset_id, title, file_plotr) %>% 
  relocate(dataset_id, title, file_plotr)

d_r <- d %>% 
  filter(!is.na(dataset_id)) %>% 
  mutate(
    r_d = glue('`{title}` = "{file_plotr}"')) %>% 
  select(dataset_id, r_d) %>% 
  nest(r_d = r_d) %>% 
  mutate(
    r = map2_chr(dataset_id, r_d, function(id, r_d){
      glue(
        'attr({id}, "plot_script") <- list(<br>
          {paste(unlist(r_d), collapse = ",<br>")})')})) %>% 
  select(-r_d)
#write_csv(d_r, here("data/tmp_dataset_plot_files_attr.csv"))

datatable_btns(d_r)
```

### Issues

- dataset `energy_density` missing `get_energy_density.R`
- dataset `ichthyo_diversity` -> `get_ichthyoplankton.R`?
- dataset `recdat` -> `get_rec.R`?
- dataset `seal_pups` missing `get_seal_pups.R`
- dataset `stock_status` missing `get_stock_status.R`; use `get_stocks.R`?
- dataset `wcr` missing `get_wcr.R`; use `get_warm_core_rings.R`?
- dataset `zoo_abund` missing `get_zoo_abund.R`; use `get_zoo_abun_anom.R`?
- dataset `zoo_diversity` missing `get_zoo_diversity.R`; use `get_zoo_div.R`?
- dataset `zoo_sli_anom` missing `get_zoo_sli_anom.R`; use `get_zoo_anom_sli.R`?
- dataset `zoo_strat_abun` missing `get_zoo_strat_abun.R`; use `get_zoo_*.R`?

Sourcing:

- dataset `seasonal_sst_anomaly_gridded`, sourcing `get_seasonal_sst_anomaly_gridded.R`:
  ```
  Error in R_nc4_open: No such file or directory
  Error in h(simpleError(msg, call)) : 
    error in evaluating the argument 'x' in selecting a method for function 'rotate': Error in nc_open trying to open file ~/github/ecodata_bbest/data-raw/sst.day.mean.2020.nc
  ```
- dataset `seasonal_oisst_anom`, sourcing `get_seasonal_oisst_anom.R`:
  ```
  Error in R_nc4_open: No such file or directory
  Error in ncdf4::nc_open(filename, readunlim = FALSE, suppress_dimvals = TRUE) : 
    Error in nc_open trying to open file ~/github/ecodata_bbest/data-raw/gridded/sst.day.mean.ltm.1982-2010.nc
  ```
- dataset `phyto_size`, sourcing `get_phyto_size.R`:
  ```
  Error in file(file, "rt") : cannot open the connection
  In addition: Warning message:
  In file(file, "rt") :
    cannot open file '~/github/ecodata_bbest/data-raw/1998_2020-OCCCI-PHYSIZE-STATS-NES_EPU_NOESTUARIES-V2021-SOE_FORMAT.csv': No such file or directory
  ```

    
## Plot scripts missing dataset

If no dataset match is found or if more than one are possible, the plot script is not assigned to a dataset, but could be manually added to the attribute section of the `get_{dataset}.R` script.

```{r}
d %>% 
  filter(is.na(dataset_id)) %>% 
  select(plot_script_ambiguous_dataset = file_plotr) %>% 
  datatable_btns()
```


## Datasets missing `plot_script`

These are datasets for which no matching plot script could be found.

```{r}
datatable_btns(tibble(
  dataset_missing_plot_script = setdiff(ds, d$dataset_id)))
```



